An Extendable \proglang{Python} Implementation of Robust Optimisation Monte Carlo

### 2021-08-24 latex_files/images/chapter4/mae2_hist_t1_romc.tex
plots after changes

title={ROMC (gradient-based) - \(\displaystyle \theta_1\)},

@@

\draw[draw=none,fill=color0] (axis cs:0.3,0) rectangle (axis cs:0.315,1.02018167274615);
\draw[draw=none,fill=color0] (axis cs:0.315,0) rectangle (axis cs:0.33,1.39039538321726);
\draw[draw=none,fill=color0] (axis cs:0.33,0) rectangle (axis cs:0.345,1.64837235793467);
\draw[draw=none,fill=color0] (axis cs:0.345,0) rectangle (axis cs:0.36,1.83766715107148);
\draw[draw=none,fill=color0] (axis cs:0.36,0) rectangle (axis cs:0.375,2.03114988210955);
\draw[draw=none,fill=color0] (axis cs:0.375,0) rectangle (axis cs:0.39,2.20118016090059);
\draw[draw=none,fill=color0] (axis cs:0.39,0) rectangle (axis cs:0.405,2.42565363240795);
\draw[draw=none,fill=color0] (axis cs:0.405,0) rectangle (axis cs:0.42,2.83858430947187);
\draw[draw=none,fill=color0] (axis cs:0.42,0) rectangle (axis cs:0.435,3.02313277298727);
\draw[draw=none,fill=color0] (axis cs:0.435,0) rectangle (axis cs:0.45,3.49050664276752);
\draw[draw=none,fill=color0] (axis cs:0.45,0) rectangle (axis cs:0.465,3.58012851385441);
\draw[draw=none,fill=color0] (axis cs:0.465,0) rectangle (axis cs:0.48,3.63066296452957);
\draw[draw=none,fill=color0] (axis cs:0.48,0) rectangle (axis cs:0.495,3.34895434170502);
\draw[draw=none,fill=color0] (axis cs:0.495,0) rectangle (axis cs:0.51,3.09544450074894);
\draw[draw=none,fill=color0] (axis cs:0.51,0) rectangle (axis cs:0.525,2.92569341781802);
\draw[draw=none,fill=color0] (axis cs:0.525,0) rectangle (axis cs:0.54,2.63923846537203);
\draw[draw=none,fill=color0] (axis cs:0.54,0) rectangle (axis cs:0.555,2.52616414203809);
\draw[draw=none,fill=color0] (axis cs:0.555,0) rectangle (axis cs:0.57,2.21569834562492);
\draw[draw=none,fill=color0] (axis cs:0.57,0) rectangle (axis cs:0.585,2.07749639488345);
\draw[draw=none,fill=color0] (axis cs:0.585,0) rectangle (axis cs:0.6,1.95995493778819);
\draw[draw=none,fill=color0] (axis cs:0.6,0) rectangle (axis cs:0.615,1.85302292337607);
\draw[draw=none,fill=color0] (axis cs:0.615,0) rectangle (axis cs:0.63,1.59560434037885);
\draw[draw=none,fill=color0] (axis cs:0.63,0) rectangle (axis cs:0.645,1.66428652195943);
\draw[draw=none,fill=color0] (axis cs:0.645,0) rectangle (axis cs:0.66,1.3535415296862);
\draw[draw=none,fill=color0] (axis cs:0.66,0) rectangle (axis cs:0.675,1.45042249313527);
\draw[draw=none,fill=color0] (axis cs:0.675,0) rectangle (axis cs:0.69,1.1846280343355);
\draw[draw=none,fill=color0] (axis cs:0.69,0) rectangle (axis cs:0.705,1.19830863147962);
\draw[draw=none,fill=color0] (axis cs:0.705,0) rectangle (axis cs:0.72,0.979977468894081);
\draw[draw=none,fill=color0] (axis cs:0.72,0) rectangle (axis cs:0.735,0.941727636062617);
\draw[draw=none,fill=color0] (axis cs:0.735,0) rectangle (axis cs:0.75,0.705807134291806);
\draw[draw=none,fill=color0] (axis cs:0.75,0) rectangle (axis cs:0.765,0.614789283904501);
\draw[draw=none,fill=color0] (axis cs:0.765,0) rectangle (axis cs:0.78,0.496689435089055);
\draw[draw=none,fill=color0] (axis cs:0.78,0) rectangle (axis cs:0.795,0.456206035376906);
\draw[draw=none,fill=color0] (axis cs:0.795,0) rectangle (axis cs:0.81,0.425773686627776);
\draw[draw=none,fill=color0] (axis cs:0.81,0) rectangle (axis cs:0.825,0.449226138874808);
\draw[draw=none,fill=color0] (axis cs:0.825,0) rectangle (axis cs:0.84,0.309907404693004);
\draw[draw=none,fill=color0] (axis cs:0.84,0) rectangle (axis cs:0.855,0.224752667367446);
\draw[draw=none,fill=color0] (axis cs:0.855,0) rectangle (axis cs:0.87,0.192924339317897);
\draw[draw=none,fill=color0] (axis cs:0.87,0) rectangle (axis cs:0.885,0.0974393551692405);
\draw[draw=none,fill=color0] (axis cs:0.885,0) rectangle (axis cs:0.9,0.176730979433038);
\draw[draw=none,fill=color0] (axis cs:0.9,0) rectangle (axis cs:0.915,0.170309474651111);
\draw[draw=none,fill=color0] (axis cs:0.915,0) rectangle (axis cs:0.93,0.145461043103651);
\draw[draw=none,fill=color0] (axis cs:0.93,0) rectangle (axis cs:0.945,0.0304323487491329);
\draw[draw=none,fill=color0] (axis cs:0.945,0) rectangle (axis cs:0.96,0.0206604936462);
\draw[draw=none,fill=color0] (axis cs:0.96,0) rectangle (axis cs:0.975,0);
\draw[draw=none,fill=color0] (axis cs:0.975,0) rectangle (axis cs:0.99,0.0217772770865351);

@@

0.503688298846839 0
0.503688298846839 3.5

@@

0.323676768279387 1
0.634437489183658 1

@@

\addlegendentry{$\sigma = 0.141$}

>>>>

title={ROMC (gradient-based) - Histogram of the parameter \(\displaystyle \theta_1\)},

@@

\draw[draw=none,fill=color0] (axis cs:0.3,0) rectangle (axis cs:0.315,1.23969307221967);
\draw[draw=none,fill=color0] (axis cs:0.315,0) rectangle (axis cs:0.33,1.22260605418476);
\draw[draw=none,fill=color0] (axis cs:0.33,0) rectangle (axis cs:0.345,1.58099417689925);
\draw[draw=none,fill=color0] (axis cs:0.345,0) rectangle (axis cs:0.36,1.86697039022021);
\draw[draw=none,fill=color0] (axis cs:0.36,0) rectangle (axis cs:0.375,1.9327905830084);
\draw[draw=none,fill=color0] (axis cs:0.375,0) rectangle (axis cs:0.39,2.28560027755721);
\draw[draw=none,fill=color0] (axis cs:0.39,0) rectangle (axis cs:0.405,2.65528249842742);
\draw[draw=none,fill=color0] (axis cs:0.405,0) rectangle (axis cs:0.42,2.76542029517717);
\draw[draw=none,fill=color0] (axis cs:0.42,0) rectangle (axis cs:0.435,3.08006607906211);
\draw[draw=none,fill=color0] (axis cs:0.435,0) rectangle (axis cs:0.45,3.37496095644731);
\draw[draw=none,fill=color0] (axis cs:0.45,0) rectangle (axis cs:0.465,3.55021219168023);
\draw[draw=none,fill=color0] (axis cs:0.465,0) rectangle (axis cs:0.48,3.48979291667414);
\draw[draw=none,fill=color0] (axis cs:0.48,0) rectangle (axis cs:0.495,3.29497485978374);
\draw[draw=none,fill=color0] (axis cs:0.495,0) rectangle (axis cs:0.51,3.21369852560985);
\draw[draw=none,fill=color0] (axis cs:0.51,0) rectangle (axis cs:0.525,2.95263129250428);
\draw[draw=none,fill=color0] (axis cs:0.525,0) rectangle (axis cs:0.54,2.68186180204391);
\draw[draw=none,fill=color0] (axis cs:0.54,0) rectangle (axis cs:0.555,2.34177450679284);
\draw[draw=none,fill=color0] (axis cs:0.555,0) rectangle (axis cs:0.57,2.16665229531096);
\draw[draw=none,fill=color0] (axis cs:0.57,0) rectangle (axis cs:0.585,1.90550699050888);
\draw[draw=none,fill=color0] (axis cs:0.585,0) rectangle (axis cs:0.6,1.80681861350051);
\draw[draw=none,fill=color0] (axis cs:0.6,0) rectangle (axis cs:0.615,1.82068989944754);
\draw[draw=none,fill=color0] (axis cs:0.615,0) rectangle (axis cs:0.63,1.66308656575326);
\draw[draw=none,fill=color0] (axis cs:0.63,0) rectangle (axis cs:0.645,1.55350554347052);
\draw[draw=none,fill=color0] (axis cs:0.645,0) rectangle (axis cs:0.66,1.55706027108261);
\draw[draw=none,fill=color0] (axis cs:0.66,0) rectangle (axis cs:0.675,1.34606411506585);
\draw[draw=none,fill=color0] (axis cs:0.675,0) rectangle (axis cs:0.69,1.25058859381965);
\draw[draw=none,fill=color0] (axis cs:0.69,0) rectangle (axis cs:0.705,1.02541420681756);
\draw[draw=none,fill=color0] (axis cs:0.705,0) rectangle (axis cs:0.72,1.08883061316133);
\draw[draw=none,fill=color0] (axis cs:0.72,0) rectangle (axis cs:0.735,0.901026681844632);
\draw[draw=none,fill=color0] (axis cs:0.735,0) rectangle (axis cs:0.75,0.90959073604536);
\draw[draw=none,fill=color0] (axis cs:0.75,0) rectangle (axis cs:0.765,0.663388353950532);
\draw[draw=none,fill=color0] (axis cs:0.765,0) rectangle (axis cs:0.78,0.635304321110202);
\draw[draw=none,fill=color0] (axis cs:0.78,0) rectangle (axis cs:0.795,0.584894248497155);
\draw[draw=none,fill=color0] (axis cs:0.795,0) rectangle (axis cs:0.81,0.541909616027169);
\draw[draw=none,fill=color0] (axis cs:0.81,0) rectangle (axis cs:0.825,0.364723435432413);
\draw[draw=none,fill=color0] (axis cs:0.825,0) rectangle (axis cs:0.84,0.337243430980688);
\draw[draw=none,fill=color0] (axis cs:0.84,0) rectangle (axis cs:0.855,0.304888876342628);
\draw[draw=none,fill=color0] (axis cs:0.855,0) rectangle (axis cs:0.87,0.11082071864216);
\draw[draw=none,fill=color0] (axis cs:0.87,0) rectangle (axis cs:0.885,0.14353193766205);
\draw[draw=none,fill=color0] (axis cs:0.885,0) rectangle (axis cs:0.9,0.12562311229572);
\draw[draw=none,fill=color0] (axis cs:0.9,0) rectangle (axis cs:0.915,0.107714286929387);
\draw[draw=none,fill=color0] (axis cs:0.915,0) rectangle (axis cs:0.93,0.0820282878821482);
\draw[draw=none,fill=color0] (axis cs:0.93,0) rectangle (axis cs:0.945,0.0827149079075519);
\draw[draw=none,fill=color0] (axis cs:0.945,0) rectangle (axis cs:0.96,0.0269285717323464);
\draw[draw=none,fill=color0] (axis cs:0.96,0) rectangle (axis cs:0.975,0.0307869571533697);
\draw[draw=none,fill=color0] (axis cs:0.975,0) rectangle (axis cs:0.99,0);

@@

0.50403516578119 0
0.50403516578119 3.5

@@

0.321847690178847 1
0.637029674539771 1

@@

\addlegendentry{$\sigma = 0.143$}

### 2021-08-24 latex_files/images/chapter4/mae2_hist_t1_romc_bo.tex
plots after changes

title={ROMC (Bayesian Optimisation) - \(\displaystyle \theta_1\)},

@@

\draw[draw=none,fill=color0] (axis cs:0.3,0) rectangle (axis cs:0.315,1.67339010906917);
\draw[draw=none,fill=color0] (axis cs:0.315,0) rectangle (axis cs:0.33,2.12285439456296);
\draw[draw=none,fill=color0] (axis cs:0.33,0) rectangle (axis cs:0.345,2.41994534810638);
\draw[draw=none,fill=color0] (axis cs:0.345,0) rectangle (axis cs:0.36,2.13421448089961);
\draw[draw=none,fill=color0] (axis cs:0.36,0) rectangle (axis cs:0.375,2.60269456308737);
\draw[draw=none,fill=color0] (axis cs:0.375,0) rectangle (axis cs:0.39,2.61479552461991);
\draw[draw=none,fill=color0] (axis cs:0.39,0) rectangle (axis cs:0.405,2.51971654115006);
\draw[draw=none,fill=color0] (axis cs:0.405,0) rectangle (axis cs:0.42,2.94571977877467);
\draw[draw=none,fill=color0] (axis cs:0.42,0) rectangle (axis cs:0.435,2.78840727885186);
\draw[draw=none,fill=color0] (axis cs:0.435,0) rectangle (axis cs:0.45,2.70814579929938);
\draw[draw=none,fill=color0] (axis cs:0.45,0) rectangle (axis cs:0.465,2.89534026545558);
\draw[draw=none,fill=color0] (axis cs:0.465,0) rectangle (axis cs:0.48,2.97807132899427);
\draw[draw=none,fill=color0] (axis cs:0.48,0) rectangle (axis cs:0.495,2.47304140381032);
\draw[draw=none,fill=color0] (axis cs:0.495,0) rectangle (axis cs:0.51,2.18508791101595);
\draw[draw=none,fill=color0] (axis cs:0.51,0) rectangle (axis cs:0.525,2.50193553644923);
\draw[draw=none,fill=color0] (axis cs:0.525,0) rectangle (axis cs:0.54,2.27646251850645);
\draw[draw=none,fill=color0] (axis cs:0.54,0) rectangle (axis cs:0.555,1.84996536408459);
\draw[draw=none,fill=color0] (axis cs:0.555,0) rectangle (axis cs:0.57,2.10951864103732);
\draw[draw=none,fill=color0] (axis cs:0.57,0) rectangle (axis cs:0.585,1.94010517958197);
\draw[draw=none,fill=color0] (axis cs:0.585,0) rectangle (axis cs:0.6,1.70154336651221);
\draw[draw=none,fill=color0] (axis cs:0.6,0) rectangle (axis cs:0.615,1.88058820551382);
\draw[draw=none,fill=color0] (axis cs:0.615,0) rectangle (axis cs:0.63,1.72549833117864);
\draw[draw=none,fill=color0] (axis cs:0.63,0) rectangle (axis cs:0.645,1.29579071757466);
\draw[draw=none,fill=color0] (axis cs:0.645,0) rectangle (axis cs:0.66,1.50076618843174);
\draw[draw=none,fill=color0] (axis cs:0.66,0) rectangle (axis cs:0.675,1.46940247180661);
\draw[draw=none,fill=color0] (axis cs:0.675,0) rectangle (axis cs:0.69,1.16860714228384);
\draw[draw=none,fill=color0] (axis cs:0.69,0) rectangle (axis cs:0.705,1.37012519556019);
\draw[draw=none,fill=color0] (axis cs:0.705,0) rectangle (axis cs:0.72,0.767793661318775);
\draw[draw=none,fill=color0] (axis cs:0.72,0) rectangle (axis cs:0.735,0.885098900664694);
\draw[draw=none,fill=color0] (axis cs:0.735,0) rectangle (axis cs:0.75,0.65715629873569);
\draw[draw=none,fill=color0] (axis cs:0.75,0) rectangle (axis cs:0.765,0.82731063538692);
\draw[draw=none,fill=color0] (axis cs:0.765,0) rectangle (axis cs:0.78,0.813727923462651);
\draw[draw=none,fill=color0] (axis cs:0.78,0) rectangle (axis cs:0.795,0.801873920328749);
\draw[draw=none,fill=color0] (axis cs:0.795,0) rectangle (axis cs:0.81,0.459095663040085);
\draw[draw=none,fill=color0] (axis cs:0.81,0) rectangle (axis cs:0.825,0.672961636247559);
\draw[draw=none,fill=color0] (axis cs:0.825,0) rectangle (axis cs:0.84,0.561583398468614);
\draw[draw=none,fill=color0] (axis cs:0.84,0) rectangle (axis cs:0.855,0.382538559466961);
\draw[draw=none,fill=color0] (axis cs:0.855,0) rectangle (axis cs:0.87,0.340555631701063);
\draw[draw=none,fill=color0] (axis cs:0.87,0) rectangle (axis cs:0.885,0.294127452759942);
\draw[draw=none,fill=color0] (axis cs:0.885,0) rectangle (axis cs:0.9,0.239055729867026);
\draw[draw=none,fill=color0] (axis cs:0.9,0) rectangle (axis cs:0.915,0.283755200017783);
\draw[draw=none,fill=color0] (axis cs:0.915,0) rectangle (axis cs:0.93,0.176575255015415);
\draw[draw=none,fill=color0] (axis cs:0.93,0) rectangle (axis cs:0.945,0.283261283220537);
\draw[draw=none,fill=color0] (axis cs:0.945,0) rectangle (axis cs:0.96,0.258071526560991);
\draw[draw=none,fill=color0] (axis cs:0.96,0) rectangle (axis cs:0.975,0.0775449371676099);
\draw[draw=none,fill=color0] (axis cs:0.975,0) rectangle (axis cs:0.99,0.0155583791132463);
\draw[draw=none,fill=color0] (axis cs:0.99,0) rectangle (axis cs:1.005,0);
\draw[draw=none,fill=color0] (axis cs:1.005,0) rectangle (axis cs:1.02,0.0172870879036073);

@@

0.500240536632723 0
0.500240536632723 3.5

@@

\addlegendentry{$\mu = 0.500$}

@@

0.293929386789429 1
0.656599793802562 1

@@

\addlegendentry{$\sigma = 0.165$}

>>>>

title={ROMC (Bayesian Optimisation) - Histogram of the parameter \(\displaystyle \theta_1\)},

@@

\draw[draw=none,fill=color0] (axis cs:0.3,0) rectangle (axis cs:0.315,1.59230812208571);
\draw[draw=none,fill=color0] (axis cs:0.315,0) rectangle (axis cs:0.33,2.04310565145056);
\draw[draw=none,fill=color0] (axis cs:0.33,0) rectangle (axis cs:0.345,2.19382815490065);
\draw[draw=none,fill=color0] (axis cs:0.345,0) rectangle (axis cs:0.36,2.20021699441589);
\draw[draw=none,fill=color0] (axis cs:0.36,0) rectangle (axis cs:0.375,2.51506116421806);
\draw[draw=none,fill=color0] (axis cs:0.375,0) rectangle (axis cs:0.39,2.44880980882892);
\draw[draw=none,fill=color0] (axis cs:0.39,0) rectangle (axis cs:0.405,2.65904829491329);
\draw[draw=none,fill=color0] (axis cs:0.405,0) rectangle (axis cs:0.42,2.73250343027527);
\draw[draw=none,fill=color0] (axis cs:0.42,0) rectangle (axis cs:0.435,2.82852250487442);
\draw[draw=none,fill=color0] (axis cs:0.435,0) rectangle (axis cs:0.45,2.82331312648089);
\draw[draw=none,fill=color0] (axis cs:0.45,0) rectangle (axis cs:0.465,2.90135211837164);
\draw[draw=none,fill=color0] (axis cs:0.465,0) rectangle (axis cs:0.48,2.88136478592358);
\draw[draw=none,fill=color0] (axis cs:0.48,0) rectangle (axis cs:0.495,2.53560317010369);
\draw[draw=none,fill=color0] (axis cs:0.495,0) rectangle (axis cs:0.51,2.3564598017404);
\draw[draw=none,fill=color0] (axis cs:0.51,0) rectangle (axis cs:0.525,2.22420707945385);
\draw[draw=none,fill=color0] (axis cs:0.525,0) rectangle (axis cs:0.54,2.33534256536061);
\draw[draw=none,fill=color0] (axis cs:0.54,0) rectangle (axis cs:0.555,2.00495652659749);
\draw[draw=none,fill=color0] (axis cs:0.555,0) rectangle (axis cs:0.57,1.74992091039568);
\draw[draw=none,fill=color0] (axis cs:0.57,0) rectangle (axis cs:0.585,1.83870977452066);
\draw[draw=none,fill=color0] (axis cs:0.585,0) rectangle (axis cs:0.6,1.6578788920657);
\draw[draw=none,fill=color0] (axis cs:0.6,0) rectangle (axis cs:0.615,1.55026416918985);
\draw[draw=none,fill=color0] (axis cs:0.615,0) rectangle (axis cs:0.63,1.62152961093496);
\draw[draw=none,fill=color0] (axis cs:0.63,0) rectangle (axis cs:0.645,1.6437730803435);
\draw[draw=none,fill=color0] (axis cs:0.645,0) rectangle (axis cs:0.66,1.66640493128548);
\draw[draw=none,fill=color0] (axis cs:0.66,0) rectangle (axis cs:0.675,1.32365272171391);
\draw[draw=none,fill=color0] (axis cs:0.675,0) rectangle (axis cs:0.69,1.14155317519524);
\draw[draw=none,fill=color0] (axis cs:0.69,0) rectangle (axis cs:0.705,1.17480604967746);
\draw[draw=none,fill=color0] (axis cs:0.705,0) rectangle (axis cs:0.72,1.20896637137188);
\draw[draw=none,fill=color0] (axis cs:0.72,0) rectangle (axis cs:0.735,1.26617555858479);
\draw[draw=none,fill=color0] (axis cs:0.735,0) rectangle (axis cs:0.75,1.10815016078187);
\draw[draw=none,fill=color0] (axis cs:0.75,0) rectangle (axis cs:0.765,1.01575133068398);
\draw[draw=none,fill=color0] (axis cs:0.765,0) rectangle (axis cs:0.78,0.778653581806476);
\draw[draw=none,fill=color0] (axis cs:0.78,0) rectangle (axis cs:0.795,0.658517776017212);
\draw[draw=none,fill=color0] (axis cs:0.795,0) rectangle (axis cs:0.81,0.522857721601219);
\draw[draw=none,fill=color0] (axis cs:0.81,0) rectangle (axis cs:0.825,0.649384569447495);
\draw[draw=none,fill=color0] (axis cs:0.825,0) rectangle (axis cs:0.84,0.571069158563703);
\draw[draw=none,fill=color0] (axis cs:0.84,0) rectangle (axis cs:0.855,0.362376122626364);
\draw[draw=none,fill=color0] (axis cs:0.855,0) rectangle (axis cs:0.87,0.275087556542002);
\draw[draw=none,fill=color0] (axis cs:0.87,0) rectangle (axis cs:0.885,0.255847252846728);
\draw[draw=none,fill=color0] (axis cs:0.885,0) rectangle (axis cs:0.9,0.406941618766892);
\draw[draw=none,fill=color0] (axis cs:0.9,0) rectangle (axis cs:0.915,0.192257669195406);
\draw[draw=none,fill=color0] (axis cs:0.915,0) rectangle (axis cs:0.93,0.204927790769102);
\draw[draw=none,fill=color0] (axis cs:0.93,0) rectangle (axis cs:0.945,0.203525138747285);
\draw[draw=none,fill=color0] (axis cs:0.945,0) rectangle (axis cs:0.96,0.113584712363094);
\draw[draw=none,fill=color0] (axis cs:0.96,0) rectangle (axis cs:0.975,0.0662010640185658);
\draw[draw=none,fill=color0] (axis cs:0.975,0) rectangle (axis cs:0.99,0.116253091726246);
\draw[draw=none,fill=color0] (axis cs:0.99,0) rectangle (axis cs:1.005,0.0456418048890116);
\draw[draw=none,fill=color0] (axis cs:1.005,0) rectangle (axis cs:1.02,0);

@@

0.502312841390367 0
0.502312841390367 3.5

@@

\addlegendentry{$\mu = 0.502$}

@@

0.294820390999603 1
0.660267860059204 1

@@

\addlegendentry{$\sigma = 0.166$}

### 2021-08-24 latex_files/images/chapter4/mae2_hist_t2_romc.tex
plots after changes

title={ROMC (gradient-based) - \(\displaystyle \theta_2\)},

@@

\draw[draw=none,fill=color0] (axis cs:-0.4,0) rectangle (axis cs:-0.375,0.0132189786765283);
\draw[draw=none,fill=color0] (axis cs:-0.375,0) rectangle (axis cs:-0.35,0.0698717444330784);
\draw[draw=none,fill=color0] (axis cs:-0.35,0) rectangle (axis cs:-0.325,0.203477850342276);
\draw[draw=none,fill=color0] (axis cs:-0.325,0) rectangle (axis cs:-0.3,0.355023998741048);
\draw[draw=none,fill=color0] (axis cs:-0.3,0) rectangle (axis cs:-0.275,0.514595955621997);
\draw[draw=none,fill=color0] (axis cs:-0.275,0) rectangle (axis cs:-0.25,0.712880635769923);
\draw[draw=none,fill=color0] (axis cs:-0.25,0) rectangle (axis cs:-0.225,0.916830592493502);
\draw[draw=none,fill=color0] (axis cs:-0.225,0) rectangle (axis cs:-0.2,0.952710677472651);
\draw[draw=none,fill=color0] (axis cs:-0.2,0) rectangle (axis cs:-0.175,1.1953733574632);
\draw[draw=none,fill=color0] (axis cs:-0.175,0) rectangle (axis cs:-0.15,1.3804390589346);
\draw[draw=none,fill=color0] (axis cs:-0.15,0) rectangle (axis cs:-0.125,1.52584782437642);
\draw[draw=none,fill=color0] (axis cs:-0.125,0) rectangle (axis cs:-0.1,1.59477535604688);
\draw[draw=none,fill=color0] (axis cs:-0.1,0) rectangle (axis cs:-0.075,1.7604846958848);
\draw[draw=none,fill=color0] (axis cs:-0.075,0) rectangle (axis cs:-0.05,1.91108663152097);
\draw[draw=none,fill=color0] (axis cs:-0.05,0) rectangle (axis cs:-0.025,2.09048705641672);
\draw[draw=none,fill=color0] (axis cs:-0.025,0) rectangle (axis cs:0,2.27366433236291);
\draw[draw=none,fill=color0] (axis cs:0,0) rectangle (axis cs:0.025,2.32654024706902);
\draw[draw=none,fill=color0] (axis cs:0.025,0) rectangle (axis cs:0.05,2.32811393500671);
\draw[draw=none,fill=color0] (axis cs:0.05,0) rectangle (axis cs:0.0750000000000001,2.26296325438667);
\draw[draw=none,fill=color0] (axis cs:0.0750000000000001,0) rectangle (axis cs:0.1,2.10968604925645);
\draw[draw=none,fill=color0] (axis cs:0.1,0) rectangle (axis cs:0.125,2.15437878668663);
\draw[draw=none,fill=color0] (axis cs:0.125,0) rectangle (axis cs:0.15,1.78361790856873);
\draw[draw=none,fill=color0] (axis cs:0.15,0) rectangle (axis cs:0.175,1.58785112912109);
\draw[draw=none,fill=color0] (axis cs:0.175,0) rectangle (axis cs:0.2,1.44590447714217);
\draw[draw=none,fill=color0] (axis cs:0.2,0) rectangle (axis cs:0.225,1.22086710205366);
\draw[draw=none,fill=color0] (axis cs:0.225,0) rectangle (axis cs:0.25,1.01125186875443);
\draw[draw=none,fill=color0] (axis cs:0.25,0) rectangle (axis cs:0.275,0.805413486505622);
\draw[draw=none,fill=color0] (axis cs:0.275,0) rectangle (axis cs:0.3,0.800220316311271);
\draw[draw=none,fill=color0] (axis cs:0.3,0) rectangle (axis cs:0.325,0.62758674954756);
\draw[draw=none,fill=color0] (axis cs:0.325,0) rectangle (axis cs:0.35,0.600834054606967);
\draw[draw=none,fill=color0] (axis cs:0.35,0) rectangle (axis cs:0.375,0.396254622708316);
\draw[draw=none,fill=color0] (axis cs:0.375,0) rectangle (axis cs:0.4,0.300574396097251);
\draw[draw=none,fill=color0] (axis cs:0.4,0) rectangle (axis cs:0.425,0.197497836179084);
\draw[draw=none,fill=color0] (axis cs:0.425,0) rectangle (axis cs:0.45,0.168384609331968);
\draw[draw=none,fill=color0] (axis cs:0.45,0) rectangle (axis cs:0.475,0.156581949799354);
\draw[draw=none,fill=color0] (axis cs:0.475,0) rectangle (axis cs:0.5,0.068455425289165);
\draw[draw=none,fill=color0] (axis cs:0.5,0) rectangle (axis cs:0.525,0.0550790778188679);
\draw[draw=none,fill=color0] (axis cs:0.525,0) rectangle (axis cs:0.55,0.066094893382642);
\draw[draw=none,fill=color0] (axis cs:0.55,0) rectangle (axis cs:0.575,0.0275395389094342);
\draw[draw=none,fill=color0] (axis cs:0.575,0) rectangle (axis cs:0.6,0.0275395389094339);

@@

0.0308218751896741 0
0.0308218751896741 3

@@

\addlegendentry{$\mu = 0.031$}

@@

-0.179871006878183 1
0.197679132295466 1

@@

\addlegendentry{$\sigma = 0.172$}

>>>>

title={ROMC (gradient-based) - Histogram of the parameter \(\displaystyle \theta_2\)},

@@

\draw[draw=none,fill=color0] (axis cs:-0.4,0) rectangle (axis cs:-0.375,0.00554428884192465);
\draw[draw=none,fill=color0] (axis cs:-0.375,0) rectangle (axis cs:-0.35,0.0609051679887177);
\draw[draw=none,fill=color0] (axis cs:-0.35,0) rectangle (axis cs:-0.325,0.172932144280507);
\draw[draw=none,fill=color0] (axis cs:-0.325,0) rectangle (axis cs:-0.3,0.33874934889258);
\draw[draw=none,fill=color0] (axis cs:-0.3,0) rectangle (axis cs:-0.275,0.484235646321314);
\draw[draw=none,fill=color0] (axis cs:-0.275,0) rectangle (axis cs:-0.25,0.665208164482786);
\draw[draw=none,fill=color0] (axis cs:-0.25,0) rectangle (axis cs:-0.225,0.92463814505837);
\draw[draw=none,fill=color0] (axis cs:-0.225,0) rectangle (axis cs:-0.2,1.12139409849263);
\draw[draw=none,fill=color0] (axis cs:-0.2,0) rectangle (axis cs:-0.175,1.18629739177248);
\draw[draw=none,fill=color0] (axis cs:-0.175,0) rectangle (axis cs:-0.15,1.38911741112759);
\draw[draw=none,fill=color0] (axis cs:-0.15,0) rectangle (axis cs:-0.125,1.3586665597235);
\draw[draw=none,fill=color0] (axis cs:-0.125,0) rectangle (axis cs:-0.1,1.4168730451184);
\draw[draw=none,fill=color0] (axis cs:-0.1,0) rectangle (axis cs:-0.075,1.86440804043856);
\draw[draw=none,fill=color0] (axis cs:-0.075,0) rectangle (axis cs:-0.05,1.77193230571172);
\draw[draw=none,fill=color0] (axis cs:-0.05,0) rectangle (axis cs:-0.025,2.14800442101592);
\draw[draw=none,fill=color0] (axis cs:-0.025,0) rectangle (axis cs:0,2.34373098482187);
\draw[draw=none,fill=color0] (axis cs:0,0) rectangle (axis cs:0.025,2.24893542723874);
\draw[draw=none,fill=color0] (axis cs:0.025,0) rectangle (axis cs:0.05,2.36527262608105);
\draw[draw=none,fill=color0] (axis cs:0.05,0) rectangle (axis cs:0.0750000000000001,2.32011000423491);
\draw[draw=none,fill=color0] (axis cs:0.0750000000000001,0) rectangle (axis cs:0.1,2.35112752816106);
\draw[draw=none,fill=color0] (axis cs:0.1,0) rectangle (axis cs:0.125,2.09237672296862);
\draw[draw=none,fill=color0] (axis cs:0.125,0) rectangle (axis cs:0.15,1.72225524667604);
\draw[draw=none,fill=color0] (axis cs:0.15,0) rectangle (axis cs:0.175,1.65885907591305);
\draw[draw=none,fill=color0] (axis cs:0.175,0) rectangle (axis cs:0.2,1.4089028988961);
\draw[draw=none,fill=color0] (axis cs:0.2,0) rectangle (axis cs:0.225,1.18892677075576);
\draw[draw=none,fill=color0] (axis cs:0.225,0) rectangle (axis cs:0.25,1.11057927007035);
\draw[draw=none,fill=color0] (axis cs:0.25,0) rectangle (axis cs:0.275,0.808010795099994);
\draw[draw=none,fill=color0] (axis cs:0.275,0) rectangle (axis cs:0.3,0.746145310081448);
\draw[draw=none,fill=color0] (axis cs:0.3,0) rectangle (axis cs:0.325,0.68232985247479);
\draw[draw=none,fill=color0] (axis cs:0.325,0) rectangle (axis cs:0.35,0.586634734027065);
\draw[draw=none,fill=color0] (axis cs:0.35,0) rectangle (axis cs:0.375,0.400470451389202);
\draw[draw=none,fill=color0] (axis cs:0.375,0) rectangle (axis cs:0.4,0.259104715630191);
\draw[draw=none,fill=color0] (axis cs:0.4,0) rectangle (axis cs:0.425,0.230773630659991);
\draw[draw=none,fill=color0] (axis cs:0.425,0) rectangle (axis cs:0.45,0.211235556781049);
\draw[draw=none,fill=color0] (axis cs:0.45,0) rectangle (axis cs:0.475,0.129869421833243);
\draw[draw=none,fill=color0] (axis cs:0.475,0) rectangle (axis cs:0.5,0.0903839207491964);
\draw[draw=none,fill=color0] (axis cs:0.5,0) rectangle (axis cs:0.525,0.0434117816322698);
\draw[draw=none,fill=color0] (axis cs:0.525,0) rectangle (axis cs:0.55,0.0482353129247447);
\draw[draw=none,fill=color0] (axis cs:0.55,0) rectangle (axis cs:0.575,0.0289411877548468);
\draw[draw=none,fill=color0] (axis cs:0.575,0) rectangle (axis cs:0.6,0.0144705938774233);

@@

0.0325607299281219 0
0.0325607299281219 3

@@

\addlegendentry{$\mu = 0.033$}

@@

-0.17677281465975 1
0.198406420501618 1

@@

\addlegendentry{$\sigma = 0.171$}
